Convective penetration probably parameterizes convective overshoot

### 2021-07-08 manuscript/ms.tex
minor manuscript clarifications

\subsection{Equations \& flux definitions}
\label{sec:theory_equations}
Throughout this work, we will utilize a modified version of the incompressible Boussinesq equations of motion,
\begin{align}
&\grad\dot\vec{u} = 0 
\label{eqn:incompressible} \\
&\partial_t \vec{u} + \vec{u}\dot\grad\vec{u} = -\frac{1}{\rho_0}\grad p + \frac{\rho_1}{\rho_0}\vec{g} + \nu\grad^2 \vec{u} 
\label{eqn:momentum} \\
&\partial_t T + \vec{u}\dot\grad T + w \gradad + \grad\dot[-k \grad \overline{T}] = \chi\grad^2 T' + Q
\label{eqn:temperature} \\
&\frac{\rho_1}{\rho_0} = -|\alpha| T.
\label{eqn:boussinesq}
\end{align}
Here, the density is decomposed into a constant background $\rho_0$ with fluctuations $\rho_1$ which appear only in the buoyancy force and depend on the temperature $T$ and the coefficient of thermal expansion $\alpha = \partial\ln\rho / \partial T$.
We furthermore define the velocity vector $\vec{u}$, the viscous diffusivity $\nu$, the thermal diffusivity $\chi$, the bulk internal heating $Q$ \citep[similar but not identical to that described in e.g.,][]{goluskin2016}, and the adiabatic temperature gradient $\gradad$.
We define $\gradad$ as a positive value to align with stellar structure conventions; thus marginal stability is achieved when $\partial_z T = -\gradad$.
The addition of a nonzero $\gradad$ to the standard Boussinesq equations was derived by \citet{spiegel_veronis_1960} and utilized by e.g., \citet{korre_etal_2019}.
In this work, we have modified the equations one step further to better model stellar environments and allow for a height-dependent radiative gradient $\gradrad$.
We allow the mean temperature profile $\overline{T}$ to carry a radiative flux $\Frad = -k \grad \overline{T}$, where $k$ is a radiative diffusivity which can vary with height.
As a result, we define $\gradrad \equiv F / k$, where $F$ is the total flux being carried by the system.
In this model, the classic thermal diffusion term $\chi \grad^2 T'$ carries no average flux and acts only on the fluctuations away from the mean temperature profile, $T' \equiv T - \overline{T}$; throughout this work, we will represent horizontal averages with bars ($\overline{\,\cdot\,}$) and fluctuations away from those averages with primes ($'$).
Crucially, we allow the mean temperature profile $\bar{T}$ which sets $\Frad$ and $T'$ to self-consistently evolve with time according to Eqn.~\ref{eqn:temperature}.

In this work, we will consider Cartesian coordinates $(x, y, z)$ with a constant vertical gravity $\vec{g} = -g\hat{z}$.
We will assume a model in which an unstable convection zone sits below a stable radiative zone, but the same logic applies to the inverted problem.
Assuming convection reaches a time-stationary state, the fluxes are found by horizontally-averaging then vertically integrating Eqn.~\ref{eqn:temperature} to find
\begin{equation}
\overline{\Ftot} = \overline{\Frad} + \overline{\Fconv} = \int Q dz + \Fbot,
\label{eqn:flux_definition}
\end{equation}
where $\Fbot$ is the flux carried at the base of the convection zone, and $\overline{\Ftot}$ is the total flux, which can vary in height due to the heating $Q$.
We note that $k$ and the temperature gradient $\justgrad \equiv -\partial_z \bar{T}$ fully specify $\Frad$ and in turn the convective flux, $\bar{\Fconv} = \bar{\Ftot} - \bar{\Frad}$.
We define the radiative gradient 
\begin{equation}
\gradrad = \frac{\bar{\Ftot}}{k}
\label{eqn:gradrad_definition}
\end{equation}
and note that the classical Schwarzschild boundary of the convection zone is the height $z = L_s$ at which $\gradrad = \gradad$ and $\bar{\Fconv} = 0$.

@@

Taking an inner product of the velocity and Eqn.~\ref{eqn:momentum} reveals the kinetic energy equation,
\begin{equation}
\frac{\partial \mathcal{K}}{\partial t}
+ \grad\dot\mathcal{F}
= \mathcal{B} - \Phi,
%\frac{\partial}{\partial t}\left(\frac{|\vec{u}|^2}{2}\right) 
%+ \grad\dot\left[\vec{u}\left(\frac{|\vec{u}|^2}{2} + \frac{p}{\rho_0}\right) - \nu\vec{u}\cross\vec{\omega}\right]
%= |\alpha| g w T - \nu|\vec{\omega}|^2,
\label{eqn:kinetic_energy}
\end{equation}
where we define the kinetic energy $\mathcal{K} \equiv |\vec{u}|^2/2$, the fluxes of kinetic energy $\mathcal{F} \equiv \left[\vec{u}(\mathcal{K} + p/\rho_0) - \nu\vec{u}\cross\vec{\omega} \right]$, the buoyant energy generation rate $\mathcal{B} \equiv |\alpha| g w T'$, and the viscous dissipation rate $\Phi \equiv \nu |\vec{\omega}|^2$ where $\vec{\omega} = \grad\cross\vec{u}$ is the vorticity and $|\vec{u}|^2 = \vec{u}\dot\vec{u}$ \& $|\vec{\omega}|^2 = \vec{\omega}\dot\vec{\omega}$.
We next take a horizontal- and time-average of Eqn.~\ref{eqn:kinetic_energy} (which we will represent with $\bar{\,\cdot\,}$ for simplicity).
Assuming that $\bar{\mathcal{K}}$ reaches a statistically stationary state, convective motions satisfy
\begin{equation}
\frac{d\bar{\mathcal{F}}}{dz} = \bar{\mathcal{B}} - \bar{\Phi}.
\label{eqn:kinetic_energy_1D}
\end{equation}
It is reasonable to assume that $\mathcal{F}$ is zero at the boundaries of the convecting region (see Fig.~\ref{fig:theory_profiles}, left panel).
We integrate Eqn.~\ref{eqn:kinetic_energy_1D} vertically between these zeros of the flux to find
\begin{equation}
\int \bar{\mathcal{B}}\,dz = \int \bar{\Phi}\,dz.
\label{eqn:integral_constraint}
\end{equation}
Integral constraints of this form are the basis for a broad range of analyses in Boussinesq convection \citep[see e.g.,][]{ahlers_etal_2009, goluskin2016} and were considered in the context of penetrative convection by \citet{roxburgh1989}.
Eqn.~\ref{eqn:integral_constraint} is the straightforward statement that work by buoyancy on large scales must be balanced by viscous dissipation on small scales.
We now find it instructive to break up the convecting region into a classical ``convection zone'' (CZ) and a extended ``penetration zone'' (PZ); we will assume that convective motions are efficient in each of these zones so that $\justgrad = \gradad$ in both the CZ and PZ.
We furthermore note that the buoyant energy generation is directly proportional to the convective flux, $\bar{\mathcal{B}} = |\alpha|g\bar{w T'} = |\alpha| g \bar{\Fconv}$.
Thus, in the PZ where $\gradad > \gradrad$, we know that $\bar{\Fconv} < 0$ and so $\bar{\mathcal{B}} < 0$ too.
Breaking up Eqn.~\ref{eqn:integral_constraint}, we see that
\begin{equation}
\int_{\rm{CZ}} \bar{\mathcal{B}}\,dz \qquad=\qquad
\int_{\rm{CZ}} \bar{\Phi}\,dz + \int_{\rm{PZ}} \bar{\Phi}\,dz + \int_{\rm{PZ}}(-\bar{\mathcal{B}})\,dz.
\label{eqn:constraint_cz_pz_split}
\end{equation}
Eqn.~\ref{eqn:constraint_cz_pz_split} is thus arranged so that the (positive) buoyant engine of convection is on the left-hand side, and the (positive) sinks of energy are on the RHS.
We see that the size of the PZ is set by some combination of viscous dissipation and buoyancy breaking, whose total effect cancels out any remaining work that dissipation in the convection zone did not itself cancel.
we now find it instructive to parameterize the fraction of the buoyant engine consumed by CZ dissipation  
\begin{equation}
f \equiv \frac{\int_{\rm{CZ}} \bar{\Phi}\,dz}{\int_{\rm{CZ}}\bar{\mathcal{B}}\,dz}.
\label{eqn:f_defn}
\end{equation}
Under this parameterization, Eqn.~\ref{eqn:constraint_cz_pz_split} can be written
\begin{equation}
\frac{\int_{\rm{PZ}} \bar{\Phi}\,dz + \int_{\rm{PZ}}(-\bar{\mathcal{B}})\,dz}{\int_{\rm{CZ}} \bar{\mathcal{B}}\,dz}
= 1 - f,
\label{eqn:first_pz_parameterization}
\end{equation}
and we can immediately read off limits on a hypothetical PZ according to $f$,
\begin{enumerate}
\item In the limit that $f \rightarrow 0$, viscous dissipation is extremely inefficient.
It is probably also reasonable to assume that $\int_{\rm{PZ}}\bar{\Phi}\,dz \rightarrow 0$, and so Eqn.~\ref{eqn:first_pz_parameterization} states that the PZ must be large enough for its negative buoyant work to be equal in magnitude to the positive buoyant work of the CZ.
This is the integral constraint on the maximum size of the PZ that \citet{roxburgh1989} derived.
\item In the limit that $f \rightarrow 1$, viscous dissipation is efficient in the CZ and cancels out the work done by buoyancy.
This is the case in standard Rayleigh-B\'{e}nard convection when the convection is contained between two hard plates.
Per Eqn.~\ref{eqn:first_pz_parameterization}, the positive-definite PZ terms must approach zero and no PZ develops in this limit.
\end{enumerate}
In general, we anticipate from the results of e.g., \citet{currie_browning_2017} that $f$ is closer to 1 than 0, but its precise value must be measured directly from simulations.
Indeed, we find that $f \gg 0$ but $f < 1$ in our simulations (see e.g., Fig.~\ref{fig:theory_profiles}, right panel).

Assuming that a PZ of depth $\delp$ develops above a CZ of depth $L_{\rm{CZ}}$, we model the PZ dissipation as
\begin{equation}
\int_{\rm{PZ}} \bar{\Phi}\,dz = \xi\frac{\delp}{L_{\rm{CZ}}}\int_{\rm{CZ}}\bar{\Phi} = \xi \delp \Phi_{\rm{CZ}}.
\label{eqn:xi_defn}
\end{equation}
Here $\Phi_{\rm{CZ}}$ is the average dissipation value in the CZ and $\xi$ is a parameter that describes the shape of the dissipation profile as a function of height in the PZ.
In other words, we assume that $\bar{\Phi} \approx \Phi_{\rm{CZ}}$ at the CZ-PZ boundary and then falls off with height.
The shape of $\bar{\Phi}$ determines the value of $\xi$, with a linear falloff producing $\xi = 1/2$, a quadratic falloff producing $\xi = 2/3$, and the in which $\bar{\Phi}$ does not decline with height produces $\xi = 1$.
Regardless, $\xi$ is another measurable parameter bounded by $[0, 1]$. 
With this parameterization, we rewrite Eqn.~\ref{eqn:first_pz_parameterization}
\begin{equation}
-\frac{\int_{\rm{PZ}}\bar{\Fconv}\,dz}{\int_{\rm{CZ}}\bar{\Fconv}\,dz} + f\xi\frac{\delp}{L_{\rm{CZ}}}
= (1 - f).
\label{eqn:theory_fraction}
\end{equation}
In order to derive a specific prediction for the PZ depth, it is necessary to specify the vertical shape of $\overline{\Fconv}$.
We will study two cases in this work, laid out below.
In both of these cases, we will define a nondimensional ``Penetration Parameter'' whose magnitude is set by the ratio of the convective flux some equidistant length $\epsilon$ both above and below the Schwarzschild convective boundary $L_s$ (assuming the region above the boundary is an adiabatic penetrative zone),
\begin{equation}
\mP \equiv -\frac{\overline{\Fconv}(z = L_s - \epsilon)}{\overline{\Fconv}(z = L_s + \epsilon)}.
\label{eqn:theory_P_defn}
\end{equation}
Since $\Fconv < 0$ in the PZ, the sign of $\mP$ is positive.
Intuitively, $\mP$ describes which terms are important in Eqn.~\ref{eqn:first_pz_parameterization}.
When $\mP \ll 1$, the buoyancy term dominates in the PZ and dissipation can be neglected there.
When $\mP \gg 1$, buoyancy is negligible in the PZ and dissipation constrains the size of the PZ.
When $\mP \sim 1$, both terms matter.

@@

In this work, we will test the predictions of Eqns.~\ref{eqn:discontinuous_prediction} and \ref{eqn:linear_prediction}.
Our goals are to see if the predicted scalings with the penetration parameter $\mP$ are realized in simulations, and to measure the dependence of $f$ on various parameters in local simulations.

\section{Simulation Details}
We nondimensionalize Eqns.~\ref{eqn:incompressible}-\ref{eqn:boussinesq} on the length scale of the Schwarzschild-unstable convection zone $L_s$, the timescale of freefall across that convection zone $\tau_{\rm{ff}}$, and the temperature scale of the internal heating over that freefall time $\Delta T$,
\begin{equation}
\begin{split}
&T^* = (\Delta T)T = Q_0 \tau_{\rm{ff}} T,\qquad
\partial_{t^*} = \tau_{\rm{ff}}^{-1}\partial_t = \left(\frac{|\alpha| g Q_0}{L_s}\right)^{1/3} \partial_t,\qquad
\grad^* = L_s^{-1} \grad,\qquad
\vec{u}^* = u_{\rm{ff}}\vec{u} = \left(|\alpha| g Q_0 L_s^2\right)^{1/3}\vec{u},
\\
&p^* = \rho_0 u_{\rm{ff}}^2\varpi,\qquad
k^* = (L_s^2 \tau_{\rm{ff}}^{-1})k,\qquad
Q^* = Q_0 Q,\qquad
\mR = \frac{u_{\rm{ff}} L_s}{\nu},\qquad
\Pran = \frac{\nu}{\chi}.
\end{split}
\end{equation}
For convenience, here we define quantities with $*$ (e.g., $T^*$) as being the ``dimensionful'' quantities of Eqns.~\ref{eqn:incompressible}-\ref{eqn:boussinesq}.
Going forward, quantities without $*$ (e.g., $T$) will be dimensionless.
The dimensionless equations of motion are therefore
\label{sec:simulation_details}
\begin{align}
&\grad\dot\vec{u} = 0 
\label{eqn:nondim_incompressible} \\
&\partial_t \vec{u} + \vec{u}\dot\grad\vec{u} = -\grad \varpi + T \hat{z} + \mR^{-1}\grad^2 \vec{u}
\label{eqn:nondim_momentum} \\
&\partial_t T + \vec{u}\dot\grad T + w \grad_{\rm{ad}}  + \grad\dot[-k \grad \overline{T}] = (\Pran\mR)^{-1}\grad^2 T' + Q.
\label{eqn:nondim_temperature}
\end{align}
We construct a domain in the range $z \in [0, L_z]$ where in this work we choose $L_z \geq 2$ so that the domain is at least twice as deep as the Schwarzschild-unstable convection zone.
We decompose the temperature field into a time-stationary initial background and fluctuations, $T(x, y, z, t) = T_0(z) + T_1(x, y, z, t)$.
For boundary conditions, we impose impenetrable, no-slip boundary conditions at the top and bottom of the box so that $\vec{u} = 0$ at $z = [0, L_z]$.
We also impose a fixed-flux boundary at the bottom of the box ($\partial_z T_1 = 0$ at $z = 0$) and a fixed temperature boundary at the top of the domain ($T_1 = 0$ at $z = L_z$).

We impose a constant internal heating which spans only part of the convection zone,
\begin{equation}
Q = \begin{cases}
0		& z < 0.1\,\,\rm{or}\,\,z\geq 0.1 + \delta_H,\\
|Q_{\rm{mag}}|		& 0.1 \leq z \leq 0.1 + \delta_H
\end{cases}.
\label{eqn:sim_Q}
\end{equation}
The integrated value of the flux through the system from the heating is therefore $F_H = \int_0^{L_z} Q_{\rm{mag}} dz = Q_{\rm{mag}}\delta_H$.
Throughout this work we choose $Q_{\rm{mag}} = 1$ and $\delta_H = 0.2$ so $F_H = 0.2$.
We offset this heating from the bottom boundary to $z = 0.1$ to avoid heating within the bottom impenetrable boundary layer where velocities go to zero and $k$ is small; this prevents strong temperature gradients from establishing there.
We assume that the (adiabatic) temperature gradient at the bottom boundary carries some flux, $\Fbot = \zeta F_H$ and we choose $\zeta = 10^{-3}$ so that most of the flux in the convection zone is carried by the convection.

In our equations, we expect the volume-average convective velocities to depend on the magnitude of the heating, $\angles{\vec{u}} \approx Q_{\rm{mag}}^{1/2} \approx 1$, so the characteristic convective frequency is $f_{\rm{conv}} \approx \angles{\vec{u}} L_s \approx 1$.
The stiffness is defined,
\begin{equation}
\mS \equiv \frac{N^2}{f_{\rm{conv}}^2} \approx N^2,
\end{equation}
where $N^2$ is the \brunt$\,$frequency in the radiative zone.
In our nondimensionalization, $N^2 = \gradad - \gradrad$ where $\gradrad = \Ftot/k$.
We treat $\mS$ as a control parameter; by choosing a value of the stiffness we set the magnitude of the background temperature gradient, $\partial_z T_0$ which in turn sets the value of $k$ in the radiative zone.

@@

We study three sweeps through the ($\mP_D$, $\mS$, $\mR$) parameter space in this paper in which we hold two of these parameters constant and vary the other.
We use reference values of $\mP_D = 4$, $\mS = 10^3$, and $\mR = 400$; all parameter space sweeps pass through these values.
According to Eqn.~\ref{eqn:discontinuous_prediction}, we expect $\delp \propto \mP_D$.

>>>>

\subsection{Equations \& flux definitions}
\label{sec:theory_equations}
Throughout this work, we will utilize a modified version of the incompressible Boussinesq equations of motion,
\begin{align}
&\grad\dot\vec{u} = 0 
\label{eqn:incompressible} \\
&\partial_t \vec{u} + \vec{u}\dot\grad\vec{u} = -\frac{1}{\rho_0}\grad p + \frac{\rho_1}{\rho_0}\vec{g} + \nu\grad^2 \vec{u} 
\label{eqn:momentum} \\
&\partial_t T + \vec{u}\dot\grad T + w \gradad + \grad\dot[-k \grad \overline{T}] = \chi\grad^2 T' + Q
\label{eqn:temperature} \\
&\frac{\rho_1}{\rho_0} = -|\alpha| T.
\label{eqn:boussinesq}
\end{align}
Here, the density is decomposed into a constant background $\rho_0$ with fluctuations $\rho_1$ which appear only in the buoyancy force and depend on the temperature $T$ and the coefficient of thermal expansion $\alpha = \partial\ln\rho / \partial T$.
We furthermore define the velocity vector $\vec{u}$, the viscous diffusivity $\nu$, the thermal diffusivity $\chi$, the bulk internal heating $Q$ \citep[similar but not identical to that described in e.g.,][]{goluskin2016}, the adiabatic gradient $\gradad$, and a height-dependent thermal conductivity $k$.
We will consider Cartesian coordinates $(x, y, z)$ with a constant vertical gravity $\vec{g} = -g\hat{z}$.
Throughout this work, we will represent horizontal averages with bars ($\overline{\,\cdot\,}$) and fluctuations away from those averages with primes ($'$).
Thus, in Eqn.~\ref{eqn:temperature}, $\bar{T}$ is the horizontally averaged temperature and $T'$ are fluctuations away from that; both of these fields evolve in time according to this equation.

Assuming convection reaches a time-stationary state, the fluxes are found by horizontally-averaging then vertically integrating Eqn.~\ref{eqn:temperature} to find
\begin{equation}
\overline{\Ftot} = \overline{\Frad} + \overline{\Fconv} = \int Q dz + \Fbot,
\label{eqn:flux_definition}
\end{equation}
where $\Fbot$ is the flux carried at the bottom of the domain, and $\overline{\Ftot}$ is the total flux, which can vary in height due to the heating $Q$.
We allow the mean temperature profile $\overline{T}$ to carry a radiative flux $\bar{\Frad} = -k \grad \overline{T}$.
We note that $k$ and $-\partial_z \bar{T}$ fully specify $\bar{\Frad}$ and in turn the convective flux, $\bar{\Fconv} = \bar{\Ftot} - \bar{\Frad}$.
We define the gradient and radiative gradient 
\begin{equation}
\justgrad \equiv -\partial_z \bar{T} \qquad
\gradrad \equiv \frac{\bar{\Ftot}}{k}.
\label{eqn:gradrad_definition}
\end{equation}
We have defined the $\justgrad$'s as positive quantities to align with stellar structure conventions.
Marginal stability is achieved when $\justgrad = \gradad$, a constant.
We note that the classical Schwarzschild boundary of the convection zone is the height $z = L_s$ at which $\gradrad = \gradad$ and $\bar{\Fconv} = 0$.

The addition of a nonzero $\gradad$ to Eqn.~\ref{eqn:temperature} was derived by \citet{spiegel_veronis_1960} and utilized by e.g., \citet{korre_etal_2019}.
In this work, we have decomposed the radiative diffusivity into a background portion ($\grad\dot \bar{\Frad}$) and a fluctuating portion ($\chi \grad^2 T'$); by doing so, we have introduced a height-dependent $\gradrad$ to the equation set while preserving the diffusive behavior on fluctuations felt by classical Rayleigh-B\'{e}nard convection.
Here, we will assume a model in which an unstable convection zone ($\gradrad > \gradad$) sits below a stable radiative zone ($\gradrad < \gradad$), but the same logic applies to the inverted problem.

@@

Taking an inner product of the velocity and Eqn.~\ref{eqn:momentum} reveals the kinetic energy equation,
\begin{equation}
\frac{\partial \mathcal{K}}{\partial t}
+ \grad\dot\mathcal{F}
= \mathcal{B} - \Phi,
%\frac{\partial}{\partial t}\left(\frac{|\vec{u}|^2}{2}\right) 
%+ \grad\dot\left[\vec{u}\left(\frac{|\vec{u}|^2}{2} + \frac{p}{\rho_0}\right) - \nu\vec{u}\cross\vec{\omega}\right]
%= |\alpha| g w T - \nu|\vec{\omega}|^2,
\label{eqn:kinetic_energy}
\end{equation}
where we define the kinetic energy $\mathcal{K} \equiv |\vec{u}|^2/2$, the fluxes of kinetic energy $\mathcal{F} \equiv \left[\vec{u}(\mathcal{K} + p/\rho_0) - \nu\vec{u}\cross\vec{\omega} \right]$, the buoyant energy generation rate $\mathcal{B} \equiv |\alpha| g w T'$, and the viscous dissipation rate $\Phi \equiv \nu |\vec{\omega}|^2$ where $\vec{\omega} = \grad\cross\vec{u}$ is the vorticity and $|\vec{u}|^2 = \vec{u}\dot\vec{u}$ \& $|\vec{\omega}|^2 = \vec{\omega}\dot\vec{\omega}$.
We next take a horizontal- and time-average of Eqn.~\ref{eqn:kinetic_energy} (which we will represent with $\bar{\,\cdot\,}$ for simplicity).
Assuming that $\bar{\mathcal{K}}$ reaches a statistically stationary state, convective motions satisfy
\begin{equation}
\frac{d\bar{\mathcal{F}}}{dz} = \bar{\mathcal{B}} - \bar{\Phi}.
\label{eqn:kinetic_energy_1D}
\end{equation}
It is reasonable to assume that $\mathcal{F}$ is zero at the boundaries of the convecting region (see Fig.~\ref{fig:theory_profiles}, left panel).
We integrate Eqn.~\ref{eqn:kinetic_energy_1D} vertically between these zeros of the flux to find
\begin{equation}
\int \bar{\mathcal{B}}\,dz = \int \bar{\Phi}\,dz.
\label{eqn:integral_constraint}
\end{equation}
Integral constraints of this form are the basis for a broad range of analyses in Boussinesq convection \citep[see e.g.,][]{ahlers_etal_2009, goluskin2016} and were considered in the context of penetrative stellar convection by \citet{roxburgh1989}.
Eqn.~\ref{eqn:integral_constraint} is the straightforward statement that work by buoyancy on large scales must be balanced by viscous dissipation on small scales.

We now find it instructive to break up the convecting region into a classical ``convection zone'' (CZ) and a extended ``penetration zone'' (PZ); we will assume that convective motions are efficient in each of these zones so that $\justgrad = \gradad$ in both the CZ and PZ.
We furthermore note that the buoyant energy generation is directly proportional to the convective flux, $\bar{\mathcal{B}} = |\alpha|g\bar{w T'} = |\alpha| g \bar{\Fconv}$.
Thus, in the PZ where $\gradad > \gradrad$, we know that $\bar{\Fconv} < 0$ and so $\bar{\mathcal{B}} < 0$ too (see the discussion around Eqn.~\ref{eqn:gradrad_definition}).
Breaking up Eqn.~\ref{eqn:integral_constraint}, we see that
\begin{equation}
\int_{\rm{CZ}} \bar{\mathcal{B}}\,dz \qquad=\qquad
\int_{\rm{CZ}} \bar{\Phi}\,dz + \int_{\rm{PZ}} \bar{\Phi}\,dz + \int_{\rm{PZ}}(-\bar{\mathcal{B}})\,dz.
\label{eqn:constraint_cz_pz_split}
\end{equation}
Eqn.~\ref{eqn:constraint_cz_pz_split} is thus arranged so that the (positive) buoyant engine of convection is on the left-hand side, and the (positive) sinks of work are on the RHS.
We see that the size of the PZ is set by some combination of viscous dissipation and buoyancy breaking.
We now parameterize the fraction of the buoyant engine consumed by CZ dissipation  
\begin{equation}
f \equiv \frac{\int_{\rm{CZ}} \bar{\Phi}\,dz}{\int_{\rm{CZ}}\bar{\mathcal{B}}\,dz}.
\label{eqn:f_defn}
\end{equation}
Under this parameterization, Eqn.~\ref{eqn:constraint_cz_pz_split} can be written
\begin{equation}
\frac{\int_{\rm{PZ}} \bar{\Phi}\,dz + \int_{\rm{PZ}}(-\bar{\mathcal{B}})\,dz}{\int_{\rm{CZ}} \bar{\mathcal{B}}\,dz}
= 1 - f,
\label{eqn:first_pz_parameterization}
\end{equation}
and we can immediately read off limits on a hypothetical PZ according to $f$,
\begin{enumerate}
\item In the limit that $f \rightarrow 0$, viscous dissipation is extremely inefficient.
It is probably also reasonable to assume that $\int_{\rm{PZ}}\bar{\Phi}\,dz \rightarrow 0$, and so Eqn.~\ref{eqn:first_pz_parameterization} states that the PZ must be large enough for its negative buoyant work to be equal in magnitude to the positive buoyant work of the CZ.
This is the integral constraint on the maximum size of the PZ that \citet{roxburgh1989} derived.
\item In the limit that $f \rightarrow 1$, viscous dissipation is efficient in the CZ and cancels out the work done by buoyancy.
This is the case in standard Rayleigh-B\'{e}nard convection when the convection is contained between two hard plates.
Per Eqn.~\ref{eqn:first_pz_parameterization}, the positive-definite PZ terms must approach zero and no PZ develops in this limit.
\end{enumerate}
In general, we anticipate from the results of e.g., \citet{currie_browning_2017} that $f$ is closer to 1 than 0, but its precise value must be measured directly from simulations.
Indeed, we find that $f \gg 0$ but $f < 1$ in our simulations (see e.g., Fig.~\ref{fig:theory_profiles}, right panel).

Assuming that a PZ of depth $\delp$ develops above a CZ of depth $L_{\rm{CZ}}$, we model the PZ dissipation as
\begin{equation}
\int_{\rm{PZ}} \bar{\Phi}\,dz = \xi\frac{\delp}{L_{\rm{CZ}}}\int_{\rm{CZ}}\bar{\Phi} = \xi \delp \Phi_{\rm{CZ}}.
\label{eqn:xi_defn}
\end{equation}
Here $\Phi_{\rm{CZ}}$ is the average dissipation value in the CZ and $\xi$ is a parameter that describes the shape of the dissipation profile as a function of height in the PZ.
In other words, we assume that $\bar{\Phi} \approx \Phi_{\rm{CZ}}$ at the CZ-PZ boundary and then falls off with height.
The shape of $\bar{\Phi}$ determines the value of $\xi$, with a linear falloff producing $\xi = 1/2$, a quadratic falloff producing $\xi = 2/3$, and if $\bar{\Phi}$ does not decline with height then $\xi = 1$.
Regardless, $\xi$ is another measurable parameter bounded by $[0, 1]$. 
With this parameterization, we rewrite Eqn.~\ref{eqn:first_pz_parameterization}
\begin{equation}
-\frac{\int_{\rm{PZ}}\bar{\Fconv}\,dz}{\int_{\rm{CZ}}\bar{\Fconv}\,dz} + f\xi\frac{\delp}{L_{\rm{CZ}}}
= (1 - f).
\label{eqn:theory_fraction}
\end{equation}
In order to derive a specific prediction for the PZ depth, it is necessary to specify the vertical shape of $\overline{\Fconv}$.
We will study two cases in this work, laid out below.
In both of these cases, we will define a nondimensional ``Penetration Parameter'' whose magnitude is set by the ratio of the convective flux some equidistant length $\epsilon$ both above and below the Schwarzschild convective boundary $L_s$ (assuming the region above the boundary is an adiabatic penetrative zone),
\begin{equation}
\mP \equiv -\frac{\overline{\Fconv}(z = L_s - \epsilon)}{\overline{\Fconv}(z = L_s + \epsilon)}.
\label{eqn:theory_P_defn}
\end{equation}
Since $\Fconv < 0$ in the PZ, the sign of $\mP$ is positive.
Intuitively, $\mP$ describes which terms are important in Eqn.~\ref{eqn:first_pz_parameterization}.
When $\mP \ll 1$, the buoyancy term dominates in the PZ and dissipation can be neglected there.
When $\mP \gg 1$, buoyancy is negligible in the PZ and dissipation constrains the size of the PZ.
When $\mP \sim 1$, both terms matter.

@@

In this work, we will test the predictions of Eqns.~\ref{eqn:discontinuous_prediction} and \ref{eqn:linear_prediction}.
Our goals are to see if the predicted scalings with the penetration parameter $\mP$ are realized in simulations, and to measure the dependence of $f$ and $\xi$ on various parameters in local simulations.

\section{Simulation Details}
We nondimensionalize Eqns.~\ref{eqn:incompressible}-\ref{eqn:boussinesq} on the length scale of the Schwarzschild-unstable convection zone $L_s$, the timescale of freefall across that convection zone $\tau_{\rm{ff}}$, and the temperature scale of the internal heating over that freefall time $\Delta T$,
\begin{equation}
\begin{split}
&T^* = (\Delta T)T = Q_0 \tau_{\rm{ff}} T,\qquad
\partial_{t^*} = \tau_{\rm{ff}}^{-1}\partial_t = \left(\frac{|\alpha| g Q_0}{L_s}\right)^{1/3} \partial_t,\qquad
\grad^* = L_s^{-1} \grad,\qquad
\vec{u}^* = u_{\rm{ff}}\vec{u} = \left(|\alpha| g Q_0 L_s^2\right)^{1/3}\vec{u},
\\
&p^* = \rho_0 u_{\rm{ff}}^2\varpi,\qquad
k^* = (L_s^2 \tau_{\rm{ff}}^{-1})k,\qquad
Q^* = Q_0 Q,\qquad
\mR = \frac{u_{\rm{ff}} L_s}{\nu},\qquad
\Pran = \frac{\nu}{\chi}.
\end{split}
\end{equation}
For convenience, here we define quantities with $*$ (e.g., $T^*$) as being the ``dimensionful'' quantities of Eqns.~\ref{eqn:incompressible}-\ref{eqn:boussinesq}.
Going forward, quantities without $*$ (e.g., $T$) will be dimensionless.
The dimensionless equations of motion are therefore
\label{sec:simulation_details}
\begin{align}
&\grad\dot\vec{u} = 0 
\label{eqn:nondim_incompressible} \\
&\partial_t \vec{u} + \vec{u}\dot\grad\vec{u} = -\grad \varpi + T \hat{z} + \mR^{-1}\grad^2 \vec{u}
\label{eqn:nondim_momentum} \\
&\partial_t T + \vec{u}\dot\grad T + w \grad_{\rm{ad}}  + \grad\dot[-k \grad \overline{T}] = (\Pran\mR)^{-1}\grad^2 T' + Q.
\label{eqn:nondim_temperature}
\end{align}
We construct a domain in the range $z \in [0, L_z]$ where in this work we choose $L_z \geq 2$ so that the domain is at least twice as deep as the Schwarzschild-unstable convection zone.
We decompose the temperature field into a time-stationary initial background and fluctuations, $T(x, y, z, t) = T_0(z) + T_1(x, y, z, t)$.
For boundary conditions, we impose impenetrable, no-slip boundary conditions at the top and bottom of the box so that $\vec{u} = 0$ at $z = [0, L_z]$.
We also impose a fixed-flux boundary at the bottom of the box ($\partial_z T_1 = 0$ at $z = 0$) and a fixed temperature boundary at the top of the domain ($T_1 = 0$ at $z = L_z$).
For a select few simulations, we impose stress-free instead of no-slip boundary conditions ($w = 0$ and $\partial_z u = \partial_z v = 0$ at $z = [0, L_z]$).

We impose a constant internal heating which spans only part of the convection zone,
\begin{equation}
Q = \begin{cases}
0		& z < 0.1\,\,\rm{or}\,\,z\geq 0.1 + \delta_H,\\
Q_{\rm{mag}}		& 0.1 \leq z \leq 0.1 + \delta_H
\end{cases}.
\label{eqn:sim_Q}
\end{equation}
The integrated value of the flux through the system from the heating is therefore $F_H = \int_0^{L_z} Q_{\rm{mag}} dz = Q_{\rm{mag}}\delta_H$.
Throughout this work we choose $Q_{\rm{mag}} = 1$ and $\delta_H = 0.2$ so $F_H = 0.2$.
We offset this heating from the bottom boundary to $z = 0.1$ to avoid heating within the bottom impenetrable boundary layer where velocities go to zero and $k$ is small; this prevents strong temperature gradients from establishing there.
We assume that the (adiabatic) temperature gradient at the bottom boundary carries some flux, $\Fbot = \zeta F_H$ and we choose $\zeta = 10^{-3}$ so that most of the flux in the convection zone is carried by the convection.

In our equations, we expect the volume-average convective velocities to depend on the magnitude of the heating, $\angles{\vec{u}} \approx Q_{\rm{mag}}^{1/2} \approx 1$, so the characteristic convective frequency is $f_{\rm{conv}} \approx \angles{\vec{u}} L_s \approx 1$.
The stiffness is defined,
\begin{equation}
\mS \equiv \frac{N^2}{f_{\rm{conv}}^2} \approx N^2,
\end{equation}
where $N^2$ is the \brunt$\,$frequency in the radiative zone.
In our nondimensionalization, $N^2 = \gradad - \gradrad$.
We treat $\mS$ as a control parameter; by choosing a value of the stiffness we set the magnitude of $\justgrad$, which in turn sets the value of $k$ in the radiative zone.

@@

We study three sweeps through the ($\mP_D$, $\mS$, $\mR$) parameter space in this paper in which we hold two of these parameters constant and vary the other.
We study an additional sweep through $\mR$ parameter space using stress-free boundaries to compare to our no-slip cases.
We use reference values of $\mP_D = 4$, $\mS = 10^3$, and $\mR = 400$; all parameter space sweeps pass through these values.
According to Eqn.~\ref{eqn:discontinuous_prediction}, we expect $\delp \propto \mP_D$.
